---
title: "Exercise1_ptB"
format: html
---

This is a Quarto document for exercise 1 part B.

Loading the relevant packages:

```{r}
#Loading packages
library(ggplot2)
```

## Creating the Sampled Data

First sample 100 values from a log-normal distribution with a mean of 5 and a standard deviation of 0.5.

```{r}
sample = rlnorm(100, meanlog = 5, sdlog = 0.5)
```

The mean of the sampled data is `r mean(sample)`.

The standard deviation of the sampled data is `r stats::sd(sample)`.

## Making the plots

Create a DataFrame for ggplot to use:

```{r}
df = data.frame(sample)
```

Now for plotting the graphs...

### Histograms

**Linear scale**

For this plot I have also included the density plots for the original population in red and the sample in black.

```{r}
ggplot(df, aes(sample)) +
  geom_histogram(bins = 100, aes(y = after_stat(density))) + 
  ggtitle("Linear scaled histogram") + 
  xlab("Value") + ylab("Density") +
  geom_density() +
  
  #plot lognormal function for comparison. Use dlnorm i
  stat_function(fun=dlnorm, args = list(meanlog = 5, sdlog = 0.5), colour = 'red')
```

**Logarithmic scale**

```{r}
df$logCounts <- log10(sample)

```

```{r}
ggplot(df, aes(logCounts)) +
  geom_histogram(bins = 100) + 
  ggtitle("Logarithmic scaled histogram") + 
  xlab("Value") + ylab("Count") + 
  annotation_logticks(sides='b')

```

### Violin Plot

```{r}
ggplot(df, aes(sample, 1)) +
  geom_violin() + 
  ggtitle("Violin plot") + 
  xlab("Value") + ylab("Frequency") + 
  geom_boxplot(width = 0.1) + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

```
